Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-15 ms.tex
last round of edits

\begin{abstract} 
The Near Earth Object Wide-field Infrared Survey Explorer (NEOWISE)
Reactivation mission released data from its first full year of observations
in 2015. This data set includes $\sim$2.5 million exposures in each of W1 and
W2, effectively doubling the amount of WISE imaging available at 3.4$\mu$m and 
4.6$\mu$m relative to the AllWISE release. We have created the first ever 
full-sky set of coadds combining all publicly available W1 and W2 exposures 
from both the AllWISE and NEOWISE-Reactivation (NEOWISER) mission phases. We 
employ an adaptation of the unWISE image coaddition framework \citep{lang14}, 
which preserves the native WISE angular resolution and is optimized for forced 
photometry. By incorporating two additional scans of the entire sky, we not 
only improve the W1/W2 depths, but also largely eliminate time-dependent 
artifacts such as off-axis scattered moonlight. We anticipate that our new 
coadds will have a broad range of applications, including target selection for 
upcoming spectroscopic cosmology surveys, identification of distant/massive 
galaxy clusters, and discovery of high-redshift quasars. In particular, our 
full-depth AllWISE+NEOWISER coadds will be an important input for the Dark 
Energy Spectroscopic Instrument (DESI) selection of luminous red galaxy and 
quasar targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the solar system.
\end{abstract}

\keywords{methods: data analysis -- surveys -- techniques: image processing}

@@

Figure \ref{fig:warp_example} provides an illustration of our polynomial 
background modeling procedure applied to a single L1b quadrant. We were able to 
recover 54\% of Moon-contaminated data in W1 and 33\% in W2. We also apply this
polynomial correction procedure to frames that we flagged as potentially 
affected by scattered light halos from bright solar system planets.

@@

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w1_large_scale.eps, width=7.0in}
  \caption{\label{fig:w1_large} A subsection of the region displayed in Figure
           \ref{fig:w2_large}, now shown in W1. Left: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Right: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. Scattered moonlight has effectively
           been completely eliminated in W1. The
           two dashed red boxes show locations where Jupiter passed through
           the WISE field of view. The imprints of such planet sightings have 
           now been removed}
 \end{center}
\end{figure*}

@@

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE data products. 
We thank Stephen Bailey for downloading the L1b images to NERSC. We thank
Doug Finkbeiner for providing access to the big-memory computers which
were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
data management and HPC assistance. We thank many members of the DECaLS/MzLS 
data team for valuable feedback, especially Arjun Dey, Doug Finkbeiner, John 
Moustakas, Bob Blum and Peter Eisenhardt.

>>>>

\begin{abstract} 
The Near Earth Object Wide-field Infrared Survey Explorer (NEOWISE)
Reactivation mission released data from its first full year of observations
in 2015. This data set includes $\sim$2.5 million exposures in each of W1 and
W2, effectively doubling the amount of WISE imaging available at 3.4$\mu$m and 
4.6$\mu$m relative to the AllWISE release. We have created the first ever 
full-sky set of coadds combining all publicly available W1 and W2 exposures 
from both the AllWISE and NEOWISE-Reactivation (NEOWISER) mission phases. We 
employ an adaptation of the unWISE image coaddition framework \citep{lang14}, 
which preserves the native WISE angular resolution and is optimized for forced 
photometry. By incorporating two additional scans of the entire sky, we not 
only improve the W1/W2 depths, but also largely eliminate time-dependent 
artifacts such as off-axis scattered moonlight. We anticipate that our new 
coadds will have a broad range of applications, including target selection for 
upcoming spectroscopic cosmology surveys, identification of distant/massive 
galaxy clusters, and discovery of high-redshift quasars. In particular, our 
full-depth AllWISE+NEOWISER coadds will be an important input for the Dark 
Energy Spectroscopic Instrument (DESI) selection of luminous red galaxy and 
quasar targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the inner solar system.
\end{abstract}

\keywords{methods: data analysis -- surveys: cosmology -- techniques: image processing}

@@

Figure \ref{fig:warp_example} provides an illustration of our polynomial 
background modeling procedure applied to a single L1b quadrant. We were able to 
recover 54\% of Moon-contaminated data in W1 and 33\% in W2. We also apply this
polynomial correction procedure to frames that we flagged as potentially 
affected by scattered light halos from bright solar system planets. We
categorically exclude \verb|qual_frame|=0 exposures, making no attempt to 
recover such frames.

@@

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w1_large_scale.eps, width=7.0in}
  \caption{\label{fig:w1_large} A subsection of the region displayed in Figure
           \ref{fig:w2_large}, now shown in W1. Left: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Right: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. Scattered moonlight (vertical streaks
           in left panel) has been completely eliminated in W1. The
           two dashed red boxes show locations where Jupiter passed through
           the WISE field of view. The imprints of such planet sightings have 
           now been removed}
 \end{center}
\end{figure*}

@@

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE/NEOWISE data 
products. We thank Stephen Bailey for downloading the L1b images to NERSC. We 
thank Doug Finkbeiner for providing access to the big-memory computers which
were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
data management and HPC assistance. We thank Ben Weaver, Debbie Bard and Rollin
Thomas for additional HPC advice. We thank many members of the DECaLS/MzLS 
data team for valuable feedback, especially Arjun Dey, Doug Finkbeiner, John 
Moustakas, Bob Blum and Peter Eisenhardt.
